workshop

### 2023-03-14 scripts/workshop/workshop.Rmd
looking at hosts over time

Data are now ready. ph only has one of every site-month combo
```{r}
ph_ab <- ph %>% pivot_longer(.,cols = c(AB2:AB42))
ph_ab %>% ggplot(.,aes(x=Month.1, y=value, color=name, group = name)) + geom_point() + geom_line() + facet_wrap(vars(WetAltID))
```

```{r}
ph_ra <- ph %>% pivot_longer(.,cols = c(RA2:RA42))
ph_ra %>% ggplot(.,aes(x=Month.1, y=value, color=name, group=name)) + geom_point() + geom_line() + facet_wrap(vars(WetAltID), ncol=1)
```

>>>>

Data are now ready. ph only has one of every site-month combo
```{r}
ph_ab <- ph %>% select(-c(ABAmb,ABSal)) %>% pivot_longer(.,cols = c(AB2:AB42))
ph_ab %>% ggplot(.,aes(x=Month.1, y=value, color=name, group = name)) + geom_point() + geom_line() + facet_wrap(vars(WetAltID))
```

```{r}
ph_ra <- ph %>% pivot_longer(.,cols = c(RA2:RA42))
ph_ra %>% ggplot(.,aes(x=Month.1, y=value, color=name, group=name)) + geom_point() + geom_line() + facet_wrap(vars(WetAltID))
```

```{r}
ph_pa <- ph %>% pivot_longer(.,cols = c(PA2:PA42))
ph_pa %>% ggplot(.,aes(x=Month.1, y=value, color=name, fill=name, group=name)) + geom_col() + facet_wrap(vars(WetAltID))
```
